Hypertension and microbiome

### 2018-12-31 rrbiome.Rmd
Better matrix

meta.merge.alphadiversity <- function(pseq, index = "shannon") {
    alphadiversity  <- microbiome::global(pseq, index = index)
    base::merge(meta(pseq), alphadiversity, by=0, all=TRUE) %>%
        dplyr::rename(Sample_ID = Row.names) %>%
            dplyr::mutate(BL_AGE_GROUP = group_age(BL_AGE))
}
```

@@

```{r temp}
dist.matrix <- as.matrix(bray.dist.m)
attr(dist.matrix, "method") <- "bray"
```

>>>>

meta.merge.alphadiversity <- function(pseq, index = "shannon") {
    alphadiversity  <- microbiome::global(pseq, index = index)
    base::merge(meta(pseq), alphadiversity, by=0, all=TRUE) %>%
        dplyr::rename(Sample_ID = Row.names) %>%
            dplyr::mutate(BL_AGE_GROUP = group_age(BL_AGE))
}

calculate.beta.matrix <- function(pseq) {
    compositional.profile <- microbiome::transform(pseq, 'compositional')
    otu <- microbiome::abundances(compositional.profile)
    bray.dist.m <- vegan::vegdist(t(otu), method="bray")
    dist.matrix <- as.matrix(bray.dist.m)
    attr(dist.matrix, "method") <- "bray"
    dist.matrix
}
```

@@
